Identity Blockchain - Proof of Identity

### 2022-07-23 paper.tex
Human readable points we need to prove in the first proof (NinOwnsKid)

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
Using https://github.com/zkp-application/circom-rsa-verify for now, MIT license.
Which probably doesn't work, we should check (sha256?).
The next line is used on a file of shape:
-----BEGIN PUBLIC KEY-----
...
-----END PUBLIC KEY-----
-----BEGIN CERTIFICATE-----
...
-----END CERTIFICATE-----
We assume: 
	modulus = Subject Modulus
	exp = Subject Exponent

openssl x509 -in Identification.pem -text -noout

@@

//hashNumberOfWords = 4 for sha256
//rsaNumberOfWords = 32 for 2048 rsa
//we use words of 64 bits
template NinOwnsKid(
		rsaNumberOfWords, 
		hashNumberOfWords, 
		lengthInBitsOfSignedMessage,
		lengthOfNinInBits
){
	//TODO: What happens to uint256 when converted to signal

@@

	var hashed[hashNumberOfWords];//4x64 bit
	var hashedBits[hashNumberOfWords*64];
	for (int i=0; i<hashNumberOfWords*64;i++){
		hashedBits[i] <== sha.out[i];
	}
	component b2n = Bits2Num(64);
	//TODO:Can we use a component multiple times?
	//Will all the constraints be generated
	for (int i=0;i<hashNumberOfWords;i++){
		for (int j=0;j<64;j++){
			b2n.in[j] <== hashedBits[i*64+j];
		}
	  hashed[i] <== b2n.out;
	}

	//lets assume sha256WithRSAEncryption

	component rsa = RsaVerifyPkcs1v15(64, rsaNumberOfWords, 17, 4);
	for (var i = 0; i < rsaNumberOfWords; i++){
		rsa.exp[i] <== exp[i];
		rsa.sign[i] <== sign[i];
		rsa.modulus[i] <== modulus[i];
	}
	for (var i = 0; i<hashNumberOfWords; i++){
		rsa.hashed[i] <== hashed[i];
	}

@@

}
component main { public [hNin,vKid]} = NinOwnsKid();
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}

>>>>

Using https://github.com/zkp-application/circom-rsa-verify for now, MIT license.
Which probably doesn't work, we should check (sha256?). \\
The next line is used on a file of shape:\\
-----BEGIN PUBLIC KEY-----\\
...\\
-----END PUBLIC KEY-----\\
-----BEGIN CERTIFICATE-----\\
...\\
-----END CERTIFICATE-----\\
We assume: \\
	modulus = Subject Modulus\\
	exp = Subject Exponent\\
openssl x509 -in Identification.pem -text -noout\\

Statements we need to check:
\begin{itemize}
	\item CA is an accepted CA by \pbc{}
		\begin{itemize}
			\item A set representation  exists on blockchain which contains CA public keys (CA-public-keys).
			\item Verify inclusion of the CA in cert in CA-public-keys.
			\item A set representation exists on blockchain which has all the revoked CA public keys (Revoked-CA-public-keys).
			\item Verify exclusion of the CA in cert from Revoked-CA-public-keys.
			\item Verify CA validity with respect to time (maybe blockchain)
		\end{itemize}
	\item Cert CA signed 
		\begin{itemize}
			\item the Kid
			\item x509 Subject that contains Nin in the right place in the subject
			\item verify Validity of x509 cert with respect to time
		\end{itemize}
	\item Kid is not on revoked certs list by CA (blockchain hosted list)
	\item Kid decrypts vKid into clear text "registerKid".
\end{itemize}

@@

//hashNumberOfWords = 4 for sha256
//rsaNumberOfWords = 32 for 2048 rsa
//we use words of 64 bits
template NinOwnsKid(
		rsaNumberOfWords, 
		hashNumberOfWords, 
		lengthInBitsOfSignedMessage,
		lengthOfNinInBits,
		bitsInAWord
){
	//TODO: What happens to uint256 when converted to signal

@@

	var hashed[hashNumberOfWords];//4x64 bit
	var hashedBits[hashNumberOfWords*bitsInAWord];
	for (int i=0; i<hashNumberOfWords*bitsInAWord;i++){
		hashedBits[i] <== sha.out[i];
	}
	component b2n = Bits2Num(64);
	//TODO:Can we use a component multiple times?
	//Will all the constraints be generated
	for (int i=0;i<hashNumberOfWords;i++){
		for (int j=0;j<bitsInAWord;j++){
			b2n.in[j] <== hashedBits[i*64+j];
		}
	  hashed[i] <== b2n.out;
	}

	//lets assume sha256WithRSAEncryption
	//verify CA signature of Kid
	component rsa = RsaVerifyPkcs1v15(bitsInAWord, rsaNumberOfWords, 17, 4);
	for (var i = 0; i < rsaNumberOfWords; i++){
		rsa.exp[i] <== exp[i];
		rsa.sign[i] <== sign[i];
		rsa.modulus[i] <== modulus[i];
	}
	for (var i = 0; i<hashNumberOfWords; i++){
		rsa.hashed[i] <== hashed[i];
	}

	//TODO: verify Kid(vKid)=="registerKid"

@@

}
component main { public [hNin,vKid]} = NinOwnsKid();
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
